\chapter{Evaluation}


\section{Evaluation setup}

-----------------------------

\textbf{Dataset 1} - 100k raw data with no traffic. Just driving straight. First one with just steering and no other training.  With 1 centre camera.

\textbf{Dataset 2} - 100k raw data with traffic and increased wait times at junctions.

\textbf{Dataset 3} - 270K raw data with normal waiting times, increased brake scenario, different weather and light conditions, also driving in different map. With segmentation and radar.

----------------------------

\subsection{Test scenario 1}

----------------

\textbf{Epsiodes} - One minute. Manually start timer and run the evaluation. Count the \# of collisions. If collided, reset episode and start again. If no collision, restart after episode duration(1 min).


\subsection{Test Scenario 2}

---------------

Loss function as constant and using dataset 3. Explain why dataset 3 is being chosen.

CNN architecture should be same!

\textbf{MSE} - output(accel, brake and steering all regression)

\textbf{CCE} - input images(center and center depth). Output(Accel, brake and steering mse)

\textbf{With no traffic} -

Drive for 1 hour and see how model responds.

\textbf{With traffic} -

drive for 1 hour and see how model responds.

Epoch training - 50
\section{Testbed setup}

\begin{enumerate}
    \item dataset constant - Only dry day data?
        or everything?
    \item CNN parameters variable.
    \item epochs, learning rate, optimizer, loss function constant
    \item activation function constant or variable?
    \item for LSTM - timesteps value?
    \item graph - training, val loss vs epochs?
    \item graph - loss vs learning rate?
    \item graph - timesteps vs loss?
    \item graph - evaluation performance comparison?
    \item graph - Accel, brake, noaction predicted vs ?
    \item graph - brake, steering predicted vs ?
    \item graph - accel, brake, steering predicted vs ?
    \item graph - accel,brake, steering, distance(radar) predicted vs ?
    \item graph - with seg camera vs without?
    \item graph - with radar vs without?
    \item graph - imbalanced vs balanced Cross entropy?


\end{enumerate}
